\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2024-02-13 Articles/Article1-Conference/root.tex
UNFILTERED REFERENCES: added all references

Local motion planning approaches employ optimization techniques, two common ones are inverse kinematics~\cite{c29,c38}, that is based on finding a least squares solution of the manipulator joint velocities, and quadratic programming (QP)~\cite{c21,c22,c23}.  Both methods are fast, suitable for real-time applications in dynamic environments and provide smooth solutions. However, since they do not plan further than one step ahead, they tend to get stuck in local minima. Therefore, they are often combined with a higher-level planner, for global static environment based \replace{motion}{path} planning, while local optimisation takes dynamic environment changes into account. In the following text we will focus on inverse kinematics based approaches.

@@

Voxel grid~\cite{xu2021voxel, elfes1989using} representation divides the space into a regular grid of volumetric elements, or voxels, which can be used to create a more manageable approximation of the environment. While this approach offers a balance between detail and computational efficiency, it can introduce discretization errors, particularly when modeling objects with smooth surfaces or intricate details. The fidelity of the representation is dependent on the size of the voxels: smaller voxels can capture more detail but require more memory and computation, while larger voxels result in coarser approximations but are more memory and computation efficient. Adaptive voxel grids have been explored~\cite{xu2021voxel}, where the voxel size can vary throughout the space to provide higher resolution in regions of interest while conserving resources in less critical areas. Nießner et al.~\cite{niessner2013realtime} proposed Voxel hashing, for more efficient memory management in sparse environments.

@@

@@

@@

>>>>

Local motion planning approaches employ optimization techniques, two common ones are inverse kinematics~\cite{c29,c38}, that is based on finding a least squares solution of the manipulator joint velocities, and quadratic programming (QP)~\cite{c21,c22, haviland2021neo, c23}.  Both methods are fast, suitable for real-time applications in dynamic environments and provide smooth solutions. However, since they do not plan further than one step ahead, they tend to get stuck in local minima. Therefore, they are often combined with a higher-level planner, for global static environment based \replace{motion}{path} planning, while local optimisation takes dynamic environment changes into account. In the following text we will focus on inverse kinematics based approaches.

@@

Voxel grid~\cite{xu2021voxel, elfes1989using} representation divides the space into a regular grid of volumetric elements, or voxels, which can be used to create a more manageable approximation of the environment. While this approach offers a balance between detail and computational efficiency, it can introduce discretization errors, particularly when modeling objects with smooth surfaces or intricate details. The fidelity of the representation is dependent on the size of the voxels: smaller voxels can capture more detail but require more memory and computation, while larger voxels result in coarser approximations but are more memory and computation efficient. Adaptive voxel grids have been explored~\cite{xu2021voxel}, where the voxel size can vary throughout the space to provide higher resolution in regions of interest while conserving resources in less critical areas. Nießner et al.~\cite{niessner2013realtime} proposed Voxel hashing, for more efficient memory management in sparse environments. Dryanovski et al.~\cite{dryanovski2010multivolume} proposed variable voxel height and saving information about occupied and about free measurements, as well as the information about number of measurements for a specific cell.

@@

Methods that allow for the dynamical distance field generation are rare. Zhou et al.~\cite{zhou2021egoplanner} propose use of pairs of points on trajectory and obstacles in their quadcopter trajectory optimization algorithm.

%\remove{The field of image processing invented many different morphological algorithms, that work on binary images and calculate a value for every pixel in image, that represents the distance from nearest occupied binary pixel~\cite{szeliski2021computer, felzenszwalb2012distance, rosenfeld1968distance}. Approaches can be seperated based on the distance metric that they use. }

@@

\bibitem{haviland2021neo} J. Haviland and P. Corke, “NEO: A Novel Expeditious Optimisation Algorithm for Reactive Motion Control of Manipulators,” IEEE Robot. Autom. Lett., vol. 6, no. 2, Art. no. 2, Apr. 2021, doi: 10.1109/LRA.2021.3056060.

@@

\bibitem{szeliski2021computer} R. Szeliski, “Computer Vision: Algorithms and Applications, 2nd Edition,” Springer, 2021.

\bibitem{rosenfeld1968distance} A. Rosenfeld and J. L. Pfaltz, “Distance functions on digital pictures,” Pattern Recognition, vol. 1, no. 1, pp. 33–61, Jul. 1968, doi: 10.1016/0031-3203(68)90013-7.

\bibitem{felzenszwalb2012distance} P. F. Felzenszwalb and D. P. Huttenlocher, “Distance Transforms of Sampled Functions,” Theory of Comput., vol. 8, no. 1, pp. 415–428, 2012, doi: 10.4086/toc.2012.v008a019.

\bibitem{zhou2021egoplanner} X. Zhou, Z. Wang, H. Ye, C. Xu, and F. Gao, “EGO-Planner: An ESDF-Free Gradient-Based Local Planner for Quadrotors,” IEEE Robot. Autom. Lett., vol. 6, no. 2, pp. 478–485, Apr. 2021, doi: 10.1109/LRA.2020.3047728.

\bibitem{dryanovski2010multivolume} I. Dryanovski, W. Morris, and J. Xiao, “Multi-volume occupancy grids: An efficient probabilistic 3D mapping model for micro aerial vehicles,” in 2010 IEEE/RSJ International Conference on Intelligent Robots and Systems, Taipei: IEEE, Oct. 2010, pp. 1553–1559, doi: 10.1109/IROS.2010.5652494.
